Carbonate chemistry at Ny-Ålesund

### 2021-12-27 awipev-CO2.Rmd
created and new names (see notes at end of script): sal_fb_mix sal_fb_mix_interp temp_insitu_11m_mix temp_insitu_11m_mix_interp

---
title: "Carbonate chemistry at Ny-Ålesund" 
author: "Jean-Pierre Gattuso and Samir Alliouane and Bernard Gentili"
date: '`r format(Sys.Date(), "%d %B %Y")`'
output: html_document
editor_options: 
  chunk_output_type: console
  markdown: 
    wrap: 72
---

@@

```{r Sal filter, fig.width=10, fig.height=4, echo=FALSE, message= FALSE}

########### Binding sal_fb + sal_insitu if we get gaps in sal_insitu = call this new column = sal_mix ########### 
d_all <- d_all %>%
  dplyr::mutate(sal_mix = ifelse(!is.na(sal_fb), sal_fb, sal_insitu_ctd_10m))
```

```{r Temp filter, fig.width=10, fig.height=4, echo=FALSE, message= FALSE}
# Create temp_mix: filling gaps in temp_insitu_11m using temp_insitu_10m
d_all <- d_all %>%
  dplyr::mutate(temp_mix = ifelse(!is.na(temp_insitu_11m), temp_insitu_11m, temp_insitu_ctd_10m))
```

@@

# interpolation of temp_mix/sal_mix in d_all in order to have a full temperature for pHinsi()
# We take temp_mix/sal_mix because of the depth (temp11m insitu + temp10m ctd)
tempmixinterp <-approx(d_all$datetime, d_all$temp_mix, xout=d_all$datetime, method="linear", rule=2)
names(tempmixinterp) <- c("datetime", "temp_mix_interp")
tempmixinterp <- as.data.frame(tempmixinterp)
d_all$temp_mix_interp <- tempmixinterp$temp_mix_interp

salmixinterp <-approx(d_all$datetime, d_all$sal_mix, xout=d_all$datetime, method="linear", rule=2)
names(salmixinterp) <- c("datetime", "sal_mix_interp")
salmixinterp <- as.data.frame(salmixinterp)
d_all$sal_mix_interp <- salmixinterp$sal_mix_interp

# ta_xts <- dplyr::select(d_all, datetime, sal_mix, sal_mix_interp)
# ta_xts <- as.xts(ta_xts, order.by = ta_xts$datetime)
# dygraph(ta_xts, group = "awipev", main="sal mix", ylab="temp") %>%
#   dySeries("sal_mix", color = "black", pointSize =4, strokeWidth = 1, label = "ta") %>%
#   dySeries("sal_mix_interp", color = "blue", strokeWidth = 1, label = "ta interp") %>%
#   dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha =0.2,hideOnMouseOut =TRUE) %>%
#       dyOptions( drawGrid = TRUE, drawPoints = TRUE,useDataTimezone = TRUE) %>%
#     dyAxis("y",valueRange = c(33, 36)) %>%
#     dyLegend(show = "follow")   %>%
#       dyRangeSelector(height = 30, dateWindow= NULL)

@@

d <- left_join(d, d_all %>%
                 dplyr::select(
                   c(closest_datetime,
                     hour,
                     sal_fb,
                     temp_fb,
                     temp_mix,
                     temp_mix_interp,
                     sal_mix,
                     sal_mix_interp,
                     temp_insitu_11m,
                     temp_insitu_ctd,
                     temp_sf,
                     depth
                   )
                 ), by = "closest_datetime") %>% 
  dplyr::select(-closest_datetime)

# Conversion of spec pH of in situ samples to in situ temp and 4 °C
pH_seafet <- d %>%
  dplyr::filter(!is.na(ph_s_sf) & !is.na(temp_mix_interp))

pH_seafet <- pH_seafet %>% 
  dplyr::mutate(
    ph_s_sf_temp_insi = pHinsi(pH = pH_seafet$ph_s_sf, 
                         ALK = pH_seafet$at_mean_interp*1e-6, Tinsi = pH_seafet$temp_mix_interp, 
                         Tlab = pH_seafet$temp_s_lab, Pinsi = 11/10, 
                         S = pH_seafet$sal_mix_interp, Pt = 0, Sit = 0, k1k2 = "l", kf = "dg", ks="d", 
                         pHscale = "T", b="u74"),
   ph_s_sf_temp_4 = pHinsi(pH = pH_seafet$ph_s_sf, # with Lueker
                         ALK = pH_seafet$at_mean_interp*1e-6, Tinsi = 4, 
                         Tlab = pH_seafet$temp_s_lab, Pinsi = 11/10, 
                         S = pH_seafet$sal_mix_interp, Pt = 0, Sit = 0, k1k2 = "l", kf = "dg", ks="d", 
                         pHscale = "T", b="u74")
  )
# Conversion of spec pH of FerryBox samples to FerryBox temp
pH_durafet <- d %>%
  tidyr::drop_na(ph_s_dur, sal_fb, temp_fb)
pH_durafet <- pH_durafet %>% 
  dplyr::mutate(
    ph_s_dur_temp_fb = pHinsi(pH = pH_durafet$ph_s_dur, 
                              ALK = pH_durafet$at_mean_interp*1e-6, Tinsi = pH_durafet$temp_fb, 
                              Tlab = pH_durafet$temp_s_lab, Pinsi = 0, S = pH_durafet$sal_fb, 
                              Pt = 0, Sit = 0, k1k2 = "l", kf = "dg", ks="d", pHscale = "T", b="u74"),
   ph_s_dur_temp_4 = pHinsi(pH = pH_durafet$ph_s_dur, # lueker
                         ALK = pH_durafet$at_mean_interp*1e-6, Tinsi = 4,
                         Tlab = pH_durafet$temp_s_lab, Pinsi = 0,
                         S = pH_durafet$sal_fb, Pt = 0, Sit = 0, k1k2 = "l", kf = "dg", ks="d",
                         pHscale = "T", b="u74")#,
   # ph_s_dur_temp_4_l = pHinsi(pH = pH_durafet$ph_s_dur, # lueker
   #                       ALK = pH_durafet$at_mean_interp*1e-6, Tinsi = 4,
   #                       Tlab = pH_durafet$temp_s_lab, Pinsi = 0,
   #                       S = pH_durafet$sal_fb, Pt = 0, Sit = 0, k1k2 = "l", kf = "dg", ks="d",
   #                       pHscale = "T", b="u74"),
   # ph_s_dur_temp_4_s20 = pHinsi(pH = pH_durafet$ph_s_dur, # Sulpis
   #                       ALK = pH_durafet$at_mean_interp*1e-6, Tinsi = 4,
   #                       Tlab = pH_durafet$temp_s_lab, Pinsi = 0,
   #                       S = pH_durafet$sal_fb, Pt = 0, Sit = 0, k1k2 = "s20", kf = "dg", ks="d",
   #                       pHscale = "T", b="u74"),       # Millero 02
   # ph_s_dur_temp_4_p18 = pHinsi(pH = pH_durafet$ph_s_dur, # Papadimitriou
   #                       ALK = pH_durafet$at_mean_interp*1e-6, Tinsi = 4,
   #                       Tlab = pH_durafet$temp_s_lab, Pinsi = 0,
   #                       S = pH_durafet$sal_fb, Pt = 0, Sit = 0, k1k2 = "p18", kf = "dg", ks="d",
   #                       pHscale = "T", b="u74"),
   # ph_s_dur_temp_4_m02 = pHinsi(pH = pH_durafet$ph_s_dur,  # Millero 02
   #                       ALK = pH_durafet$at_mean_interp*1e-6, Tinsi = 4,
   #                       Tlab = pH_durafet$temp_s_lab, Pinsi = 0,
   #                       S = pH_durafet$sal_fb, Pt = 0, Sit = 0, k1k2 = "m02", kf = "dg", ks="d",
   #                       pHscale = "T", b="u74")

# Make mean for replicates + SD
pH_seafet_mean <- pH_seafet %>%
  dplyr::select(datetime, ph_s_sf_temp_insi, ph_s_sf_temp_4) %>% 
  dplyr::group_by(datetime) %>% 
  dplyr::summarise(ph_s_sf_temp_insi_mean = mean(ph_s_sf_temp_insi, na.rm = TRUE),
                   ph_s_sf_temp_insi_sd = sd(ph_s_sf_temp_insi, na.rm = TRUE),
                   ph_s_sf_temp_4_mean = mean(ph_s_sf_temp_4, na.rm = TRUE)
                   )
pH_durafet_mean <- pH_durafet %>%
  dplyr::select(datetime, ph_s_dur_temp_fb, ph_s_dur_temp_4) %>% 
  dplyr::group_by(datetime) %>% 
  dplyr::summarize(ph_s_dur_temp_fb_mean = mean(ph_s_dur_temp_fb, na.rm = TRUE),
                   ph_s_dur_temp_fb_sd = sd(ph_s_dur_temp_fb, na.rm = TRUE),
                   ph_s_dur_temp_4_mean = mean(ph_s_dur_temp_4, na.rm = TRUE))

#bind all spectro measurements, just to assess sd, change name of dataframe only to do the rbind.
# seafetph <- pH_seafet_mean
# colnames(seafetph) <- c("date", "mean", "sd")
# durafetph <- pH_durafet_mean
# colnames(durafetph) <- c("date", "mean", "sd")
#pH_seafet_durafet <- rbind(seafetph, durafetph)
# #calculations for all pH spectro measurement for sd
# sd_min <- min(pH_seafet_durafet$sd)
# sd_max <- max(pH_seafet_durafet$sd)
# sd_mean <- mean(pH_seafet_durafet$sd)

#put back the right column name for the following script
pH_durafet_mean$ph_s_dur_temp_fb <- pH_durafet_mean$ph_s_dur_temp_fb_mean
pH_seafet_mean$ph_s_sf_temp_insi <- pH_seafet_mean$ph_s_sf_temp_insi_mean

#  make means in "d" to have same format and call it "discrete"
discrete <- d %>%
  group_by(datetime) %>%
#dplyr::select( datetime, date,hour,sal_fb,sal_mix_interp ,sal_mix,temp_fb, at_mean_interp,at ,ct_mean_interp,ct, temp_mix,temp_mix_interp,temp_insitu_11m) %>%
  summarise(datetime = mean(datetime, na.rm = TRUE),
    sal_fb = mean(sal_fb, na.rm = TRUE),
    sal_mix = mean(sal_mix, na.rm = TRUE),
    sal_mix_interp = mean(sal_mix_interp, na.rm = TRUE),
    temp_fb = mean(temp_fb, na.rm = TRUE),
     temp_mix = mean(temp_mix, na.rm = TRUE),
    temp_mix_interp = mean(temp_mix_interp, na.rm = TRUE),
        temp_insitu_11m = mean(temp_insitu_11m, na.rm = TRUE),
    at_mean_interp = mean(at_mean_interp, na.rm = TRUE),
    at = mean(at, na.rm = TRUE),
    ct_mean_interp = mean(ct_mean_interp, na.rm = TRUE),
    ct = mean(ct, na.rm = TRUE) ,.groups = 'drop_last'
  )

# library("RColorBrewer")
# d_xts <- dplyr::select(discrete, datetime, sal_fb, sal_mix,temp_fb,temp_mix,temp_insitu_11m, at_mean_interp,at,ct_mean_interp,ct)
# d_xts <- as.xts(d_xts, order.by = d_xts$datetime)
# dygraph(d_xts, group = "awipev", main="Salinity (in FerryBox)", ylab="Salinity") %>%
#             dySeries("sal_mix", color = brewer.pal(n=9, name = "Paired")[1], strokeWidth = 1, pointSize = 4, label = "sal_mix") %>%
#             dySeries("sal_fb", color = brewer.pal(n=9, name = "Paired")[2], strokeWidth = 1, pointSize = 2, label = "sal_fb") %>%
#    dySeries("temp_mix", color = brewer.pal(n=9, name = "Paired")[3], strokeWidth = 1, pointSize = 4, label = "temp_mix") %>%
#    dySeries("temp_fb", color = brewer.pal(n=9, name = "Paired")[4], strokeWidth = 1, pointSize = 2, label = "temp_fb") %>%
#    dySeries("temp_insitu_11m", color = brewer.pal(n=9, name = "Paired")[5], strokeWidth = 1, pointSize = 2, label = "temp_insitu_11m") %>%
#     dySeries(axis="y2", "at_mean_interp", color = brewer.pal(n=9, name = "Paired")[6], strokeWidth = 1, pointSize = 4, label = "at_mean_interp") %>%
#    dySeries(axis="y2","ct_mean_interp", color =brewer.pal(n=9, name = "Paired")[7], strokeWidth = 1, pointSize = 4, label = "ct_mean_interp") %>%
#  dySeries(axis="y2","at", color = brewer.pal(n=9, name = "Paired")[8], strokeWidth = 1, pointSize = 2, label = "at") %>%
#    dySeries(axis="y2","ct", color =brewer.pal(n=9, name = "Paired")[9], strokeWidth = 1, pointSize = 2, label = "ct") %>%
#   dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha =0.2,hideOnMouseOut =TRUE) %>%
#       dyOptions( drawGrid = TRUE, drawPoints = TRUE,useDataTimezone = TRUE) %>%
#     dyLegend(show = "follow")   %>%
#    # dyAxis("y",valueRange = c(30, 37)) %>%
#       dyRangeSelector(height = 30, dateWindow= NULL)

@@

Several salinity sensors are on site, 1 inside the Ferrybox (SBE45) and
5 outside (ctd183, ctd181, ctd578, ctd964/964b and ctd103) that are
switched periodically. Salinity from FB is taken in consideration. If
data gaps are encountered, they are filled with bottom salinity data
from ctd (> 8 m). New column "sal_mix" is created and is the one used in
ESSD paper.

@@

```{r Salinity, echo=FALSE, message= FALSE, warning=FALSE, out.width="80%",fig.show='hold', fig.align="center"}
# SAL FerryBox and sal_mix
sal_xts <- dplyr::select(d_all, datetime, sal_fb, sal_mix)
sal_xts <- as.xts(sal_xts, order.by = sal_xts$datetime)
dygraph(sal_xts, group = "awipev", main="Salinity (in FerryBox)", ylab="Salinity") %>%
            dySeries("sal_fb", color = "blue", strokeWidth = 0, label = "sal_fb") %>%
            dySeries("sal_mix", color = "red", strokeWidth = 0, label = "sal_mix") %>%
dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha =0.2,hideOnMouseOut =TRUE) %>%
      dyOptions( drawGrid = TRUE, drawPoints = TRUE, pointSize = 2,useDataTimezone = TRUE) %>%
    dyLegend(show = "follow")   %>%
    dyAxis("y",valueRange = c(30, 37)) %>%
      dyRangeSelector(height = 30, dateWindow= NULL)
# now remove outliers
d_all <- d_all %>%
  dplyr::mutate(
    sal_mix = case_when(
      date > as.Date("2016-02-01") &
        date <  as.Date("2016-02-09") & sal_mix < 34 ~ NA_real_,
      date == as.Date("2015-11-19") & sal_mix < 33 ~ NA_real_,
      date > as.Date("2015-10-01") &
        date <  as.Date("2015-10-05") & sal_mix < 31.5 ~ NA_real_,
      date == as.Date("2017-03-22") &
        sal_mix < 34 ~ NA_real_,
      TRUE ~ sal_mix
    )
  )
```

@@

Several temperature sensors are on site, 1 inside the Ferrybox (SBE45),
5 outside (ctd183, ctd181, ctd578, ctd964/964b and ctd103) that are
switched periodically and 1 fixed at 11 m depth (sbe38). Temperature in
situ at 11 m depth is taken in consideration. If data gaps are
encountered, they are filled with bottom temperature data from ctd (> 8
m). New column "temp_mix" is created. For the moment, no gaps are
encountered and temp_mix = temp_insitu_11m.

@@

```{r Discrete salinity vs TA, echo=FALSE, fig.align="center", message=FALSE, warning=FALSE, out.width="100%"}
d_all_at_discrete <- d_all %>% #  To remove an outlier in red
  dplyr::select(datetime, monthd,closest_datetime, at, sal_mix)

fit <- lm(data = d_all_at_discrete, at ~ sal_mix)
slope_s_at <- fit$coefficients[[2]]
intercept_s_at <- fit$coefficients[[1]]
at_s <- ggplot(d_all_at_discrete,aes(x=sal_mix, y= at, label = monthd))+
  geom_text( aes(color=factor(monthd))) +
  scale_color_discrete(guide="none")+
    labs(x="Salinity", y="Discrete AT", color = "Months")  +
    stat_smooth(method = "lm", col = "black") +
    labs(title = paste("", "\nAdj R2 = ",signif(summary(fit)$adj.r.squared, 5),
                       ";\nIntercept =",signif(fit$coef[[1]],5 ),
                       ";\nSlope =",signif(fit$coef[[2]], 5),
                       ";\nP =", signif(summary(fit)$coef[2,4], 5),
                       ";\nRMSE =", signif(sqrt(mean(fit$residuals^2)), 5))) +
  theme_bw() +
  theme(aspect.ratio=1,
        axis.text=element_text(size=7),
        axis.title.y= element_text(size =7),
        axis.title.x= element_text(size =7),
        plot.margin = unit(c(0.5,1,1,1), "cm"),
        plot.title = element_text(size=7, hjust=0.05,margin = margin(l = 10, b = -70)))
ggsave(filename = "figures/at_s.png", plot = at_s, width = 25, height = 20, units = "cm")

# Same plot for paper
p_at_s <- ggplot(d_all_at_discrete,aes(x=sal_mix, y= at)) +
  geom_point(col="blue", size = 0.2) +
  labs(x="Salinity", y="Discrete AT")  +
  stat_smooth(method = "lm", col = "blue", size = 0.3) +
  theme_bw(base_size = 9) +
  theme(aspect.ratio=1#,
        #axis.text=element_text(size=7),
        #axis.title.y= element_text(size =7),
        #axis.title.x= element_text(size =7),
        #plot.margin = unit(c(0.5,1,1,1), "cm"),
        #plot.title = element_text(size=7, hjust=0.05,margin = margin(l = 10, b = -70))
        )
ggsave(filename = "figures/p_at_s.png", plot = p_at_s, width = 7, height = 7, units = "cm")

# Salinity is a predictor of AT -> using the regression defined above
d_all$at_calc <- slope_s_at * d_all$sal_mix + intercept_s_at
```

@@

# add here the new periods sfinterv[..]
d_all <- d_all %>%
  dplyr::mutate(deployment_sf = ifelse(datetime >= sfinterv[1] & datetime <= sfinterv[2], 01,
                                ifelse(datetime >= sfinterv[2] & datetime <= sfinterv[3], 02,
                                ifelse(datetime >= sfinterv[3], 03, NA ))))
# dygraph to check seafet data
# pH_xts <-
#   dplyr::select(d_all, datetime, voltINT, voltEXT, sal_fb, temp_insitu_ctd, ph_s_sf_temp_insi)
# pH_xts <-
#   as.xts(pH_xts, order.by = d_all$datetime)
# dygraph(pH_xts,
#         group = "awipev",
#         main = "pH",
#         ylab = "pH") %>%
#   dySeries(
#     axis = "y2",
#     "voltINT",
#     label = "voltINT",
#     color =  RColorBrewer::brewer.pal(5, "Dark2")[1],
#     strokeWidth = 0,
#     pointSize = 2
#   ) %>%
#   dySeries(axis="y2",
#     "voltEXT",
#     label = "voltEXT",
#     color =  RColorBrewer::brewer.pal(5, "Dark2")[2],
#     strokeWidth = 0,
#     pointSize = 2
#   ) %>%
#    dySeries(
#     "temp_insitu_ctd",
#     label = "temp_insitu_ctd",
#     color =  RColorBrewer::brewer.pal(5, "Dark2")[3],
#     strokeWidth = 0,
#     pointSize = 2
#   ) %>%
#    dySeries(
#     "sal_fb",
#     label = "sal_fb",
#     color =  RColorBrewer::brewer.pal(5, "Dark2")[4],
#     strokeWidth = 0,
#     pointSize = 2
#   ) %>%
#    dySeries(
#     "ph_s_sf_temp_insi",
#     label = "ph_s_sf_temp_insi",
#     color =  RColorBrewer::brewer.pal(5, "Dark2")[5],
#     strokeWidth = 0,
#     pointSize = 4
#   ) %>%
#   dyHighlight(
#     highlightCircleSize = 8,
#     highlightSeriesBackgroundAlpha = 0.5,
#     hideOnMouseOut = TRUE
#   ) %>%
#   dyLegend(show = "follow")   %>%
#   dyAxis("y2",valueRange = c(-2,2))%>%
#   dyOptions(
#     drawGrid = TRUE,
#     drawPoints = TRUE,
#     pointSize = c(1, 8, 1),
#     useDataTimezone = TRUE
#   ) %>%
#   dyRangeSelector(height = 30, dateWindow = NULL)

@@

calib_spectro <- cbind(calib_spectro_all, calib_spectro_10m)
kbl(calib_spectro)%>%
    kable_paper() %>% 
    kable_styling(fixed_thead = T)
```

@@

```{r seafet profiles, eval=FALSE, echo=FALSE, message= FALSE, warning=FALSE, out.width="80%",fig.show='hold', fig.align="center"}

@@

range_month <-
  d_all %>%
  dplyr::select(montht, sal_mix, temp_mix, temp_insitu_11m, pHint_tot_sf_10m) %>% 
  group_by(montht) %>%
  my_skim()
kable(range_month, caption = "")
```

@@

-   sal_mix: when ferrybox data (sal_fb) are missing, they are replaced
    by data from the profiling ctd for depths > 8 m (sal_insitu_ctd_10m)

-   sal_mix_interp: interpolated salinity sal_mix. It is used to have as
    many spec pH to display (some are during missing data)

>>>>

---
title: "Carbonate chemistry at Ny-Ålesund" 
author: "Jean-Pierre Gattuso and Samir Alliouane and Philipp Fisher"
date: '`r format(Sys.Date(), "%d %B %Y")`'
output: html_document
editor_options: 
  chunk_output_type: console
  markdown: 
    wrap: 72
---

@@

```{r sal and temp data, fig.width=10, fig.height=4, echo=FALSE, message= FALSE}
### Fill gaps in sal_fb using sal_insitu_ctd_10m; new column = sal_fb_mix ###
### Fill gaps in sal_insitu_ctd using sal_fb_mix; new column = sal_insitu_ctd_mix ###
### Fill gaps in temp_insitu_11m using temp_insitu_ctd_10m; new column = temp_insitu_11m_mix ###
d_all <- d_all %>%
  dplyr::mutate(sal_fb_mix = ifelse(!is.na(sal_fb), sal_fb, sal_insitu_ctd_10m),
                sal_insitu_ctd_mix = ifelse(!is.na(sal_insitu_ctd), sal_insitu_ctd, sal_fb_mix),
                temp_insitu_11m_mix = ifelse(!is.na(temp_insitu_11m), temp_insitu_11m, temp_insitu_ctd_10m)
                )
```

@@

# interpolation of temp_insitu_11m_mix/sal_fb_mix in d_all in order to have a full temperature for pHinsi()
# We take temp_insitu_11m_mix/sal_fb_mix because of the depth (temp11m insitu + temp10m ctd)
tempmixinterp <-approx(d_all$datetime, d_all$temp_insitu_11m_mix, xout=d_all$datetime, method="linear", rule=2)
names(tempmixinterp) <- c("datetime", "temp_insitu_11m_mix_interp")
tempmixinterp <- as.data.frame(tempmixinterp)
d_all$temp_insitu_11m_mix_interp <- tempmixinterp$temp_insitu_11m_mix_interp

salmixinterp <-approx(d_all$datetime, d_all$sal_fb_mix, xout=d_all$datetime, method="linear", rule=2)
names(salmixinterp) <- c("datetime", "sal_fb_mix_interp")
salmixinterp <- as.data.frame(salmixinterp)
d_all$sal_fb_mix_interp <- salmixinterp$sal_fb_mix_interp

@@

d <- left_join(d, d_all %>%
                 dplyr::select(
                   c(closest_datetime,
                     hour,
                     sal_fb,
                     temp_fb,
                     temp_insitu_11m_mix,
                     temp_insitu_11m_mix_interp,
                     sal_fb_mix,
                     sal_fb_mix_interp,
                     temp_insitu_11m,
                     temp_insitu_ctd,
                     temp_sf,
                     depth
                   )
                 ), by = "closest_datetime") %>% 
  dplyr::select(-closest_datetime)

# Conversion of spec pH of in situ samples to in situ temp and 4 °C
pH_seafet <- d %>%
  dplyr::filter(!is.na(ph_s_sf) & !is.na(temp_insitu_11m_mix_interp))

pH_seafet <- pH_seafet %>% 
  dplyr::mutate(
    ph_s_sf_temp_insi = pHinsi(pH = pH_seafet$ph_s_sf, 
                         ALK = pH_seafet$at_mean_interp*1e-6, 
                         Tinsi = pH_seafet$temp_insitu_11m_mix_interp, 
                         Tlab = pH_seafet$temp_s_lab, Pinsi = 11/10, 
                         S = pH_seafet$sal_fb_mix_interp, Pt = 0, Sit = 0, 
                         k1k2 = "l", kf = "dg", ks="d", 
                         pHscale = "T", b="u74"),
   ph_s_sf_temp_4 = pHinsi(pH = pH_seafet$ph_s_sf, # with Lueker
                         ALK = pH_seafet$at_mean_interp*1e-6, Tinsi = 4, 
                         Tlab = pH_seafet$temp_s_lab, Pinsi = 11/10, 
                         S = pH_seafet$sal_fb_mix_interp, Pt = 0, Sit = 0, 
                         k1k2 = "l", kf = "dg", ks="d", 
                         pHscale = "T", b="u74")
  )
# Conversion of spec pH of FerryBox samples to FerryBox temp
pH_durafet <- d %>%
  tidyr::drop_na(ph_s_dur, sal_fb, temp_fb)
pH_durafet <- pH_durafet %>% 
  dplyr::mutate(
    ph_s_dur_temp_fb = pHinsi(pH = pH_durafet$ph_s_dur, 
                              ALK = pH_durafet$at_mean_interp*1e-6, Tinsi = pH_durafet$temp_fb, 
                              Tlab = pH_durafet$temp_s_lab, Pinsi = 0, S = pH_durafet$sal_fb, 
                              Pt = 0, Sit = 0, k1k2 = "l", kf = "dg", ks="d", pHscale = "T", b="u74"),
    ph_s_dur_temp_4 = pHinsi(pH = pH_durafet$ph_s_dur,
                             ALK = pH_durafet$at_mean_interp * 1e-6, Tinsi = 4,
                             Tlab = pH_durafet$temp_s_lab, Pinsi = 0,
                             S = pH_durafet$sal_fb, Pt = 0, Sit = 0, k1k2 = "l", 
                             kf = "dg", ks = "d",
                             pHscale = "T", b = "u74")
   )

# Make mean for replicates + SD
pH_seafet_mean <- pH_seafet %>%
  dplyr::select(datetime, ph_s_sf_temp_insi, ph_s_sf_temp_4) %>% 
  dplyr::group_by(datetime) %>% 
  dplyr::summarise(ph_s_sf_temp_insi_mean = mean(ph_s_sf_temp_insi, na.rm = TRUE),
                   ph_s_sf_temp_insi_sd = sd(ph_s_sf_temp_insi, na.rm = TRUE),
                   ph_s_sf_temp_4_mean = mean(ph_s_sf_temp_4, na.rm = TRUE)
                   )
pH_durafet_mean <- pH_durafet %>%
  dplyr::select(datetime, ph_s_dur_temp_fb, ph_s_dur_temp_4) %>% 
  dplyr::group_by(datetime) %>% 
  dplyr::summarize(ph_s_dur_temp_fb_mean = mean(ph_s_dur_temp_fb, na.rm = TRUE),
                   ph_s_dur_temp_fb_sd = sd(ph_s_dur_temp_fb, na.rm = TRUE),
                   ph_s_dur_temp_4_mean = mean(ph_s_dur_temp_4, na.rm = TRUE))
# put back the right column name for the following script
pH_durafet_mean$ph_s_dur_temp_fb <- pH_durafet_mean$ph_s_dur_temp_fb_mean
pH_seafet_mean$ph_s_sf_temp_insi <- pH_seafet_mean$ph_s_sf_temp_insi_mean

# make means in "d" to have same format and call it "discrete"
discrete <- d %>%
  group_by(datetime) %>%
#dplyr::select( datetime, date,hour,sal_fb,sal_fb_mix_interp ,sal_fb_mix,temp_fb, at_mean_interp,at ,ct_mean_interp,ct, temp_insitu_11m_mix,temp_insitu_11m_mix_interp,temp_insitu_11m) %>%
  summarise(datetime = mean(datetime, na.rm = TRUE),
    sal_fb = mean(sal_fb, na.rm = TRUE),
    sal_fb_mix = mean(sal_fb_mix, na.rm = TRUE),
    sal_fb_mix_interp = mean(sal_fb_mix_interp, na.rm = TRUE),
    temp_fb = mean(temp_fb, na.rm = TRUE),
     temp_insitu_11m_mix = mean(temp_insitu_11m_mix, na.rm = TRUE),
    temp_insitu_11m_mix_interp = mean(temp_insitu_11m_mix_interp, na.rm = TRUE),
        temp_insitu_11m = mean(temp_insitu_11m, na.rm = TRUE),
    at_mean_interp = mean(at_mean_interp, na.rm = TRUE),
    at = mean(at, na.rm = TRUE),
    ct_mean_interp = mean(ct_mean_interp, na.rm = TRUE),
    ct = mean(ct, na.rm = TRUE) ,.groups = 'drop_last'
  )

@@

Several salinity sensors are on site, 1 inside the Ferrybox (SBE45) and
5 outside (ctd183, ctd181, ctd578, ctd964/964b and ctd103) that are
switched periodically. Salinity from FB is taken in consideration. If
data gaps are encountered, they are filled with bottom salinity data
from ctd (> 8 m). New column "sal_fb_mix" is created and is the one used in
ESSD paper.

@@

```{r Salinity, echo=FALSE, message= FALSE, warning=FALSE, out.width="80%",fig.show='hold', fig.align="center"}
# SAL FerryBox and sal_fb_mix
sal_xts <- dplyr::select(d_all, datetime, sal_fb, sal_fb_mix)
sal_xts <- as.xts(sal_xts, order.by = sal_xts$datetime)
dygraph(sal_xts, group = "awipev", main="Salinity (in FerryBox)", ylab="Salinity") %>%
            dySeries("sal_fb", color = "blue", strokeWidth = 0, label = "sal_fb") %>%
            dySeries("sal_fb_mix", color = "red", strokeWidth = 0, label = "sal_fb_mix") %>%
dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha =0.2,hideOnMouseOut =TRUE) %>%
      dyOptions( drawGrid = TRUE, drawPoints = TRUE, pointSize = 2,useDataTimezone = TRUE) %>%
    dyLegend(show = "follow")   %>%
    dyAxis("y",valueRange = c(30, 37)) %>%
      dyRangeSelector(height = 30, dateWindow= NULL)
# now remove outliers
d_all <- d_all %>%
  dplyr::mutate(
    sal_fb_mix = case_when(
      date > as.Date("2016-02-01") &
        date <  as.Date("2016-02-09") & sal_fb_mix < 34 ~ NA_real_,
      date == as.Date("2015-11-19") & sal_fb_mix < 33 ~ NA_real_,
      date > as.Date("2015-10-01") &
        date <  as.Date("2015-10-05") & sal_fb_mix < 31.5 ~ NA_real_,
      date == as.Date("2017-03-22") &
        sal_fb_mix < 34 ~ NA_real_,
      TRUE ~ sal_fb_mix
    )
  )
```

@@

Several temperature sensors are on site, 1 inside the Ferrybox (SBE45),
5 outside (ctd183, ctd181, ctd578, ctd964/964b and ctd103) that are
switched periodically and 1 fixed at 11 m depth (sbe38). Temperature in
situ at 11 m depth is taken in consideration. If data gaps are
encountered, they are filled with bottom temperature data from ctd (> 8
m). New column "temp_insitu_11m_mix" is created. For the moment, no gaps are
encountered and temp_insitu_11m_mix = temp_insitu_11m.

@@

```{r Discrete salinity vs TA, echo=FALSE, fig.align="center", message=FALSE, warning=FALSE, out.width="100%"}
d_all_at_discrete <- d_all %>% #  To remove an outlier in red
  dplyr::select(datetime, monthd,closest_datetime, at, sal_fb_mix)

fit <- lm(data = d_all_at_discrete, at ~ sal_fb_mix)
slope_s_at <- fit$coefficients[[2]]
intercept_s_at <- fit$coefficients[[1]]
at_s <- ggplot(d_all_at_discrete,aes(x=sal_fb_mix, y= at, label = monthd))+
  geom_text( aes(color=factor(monthd))) +
  scale_color_discrete(guide="none")+
    labs(x="Salinity", y="Discrete AT", color = "Months")  +
    stat_smooth(method = "lm", col = "black") +
    labs(title = paste("", "\nAdj R2 = ",signif(summary(fit)$adj.r.squared, 5),
                       ";\nIntercept =",signif(fit$coef[[1]],5 ),
                       ";\nSlope =",signif(fit$coef[[2]], 5),
                       ";\nP =", signif(summary(fit)$coef[2,4], 5),
                       ";\nRMSE =", signif(sqrt(mean(fit$residuals^2)), 5))) +
  theme_bw() +
  theme(aspect.ratio=1,
        axis.text=element_text(size=7),
        axis.title.y= element_text(size =7),
        axis.title.x= element_text(size =7),
        plot.margin = unit(c(0.5,1,1,1), "cm"),
        plot.title = element_text(size=7, hjust=0.05,margin = margin(l = 10, b = -70)))
ggsave(filename = "figures/at_s.png", plot = at_s, width = 25, height = 20, units = "cm")

# Same plot for paper
p_at_s <- ggplot(d_all_at_discrete,aes(x=sal_fb_mix, y= at)) +
  geom_point(col="blue", size = 0.2) +
  labs(x="Salinity", y="Discrete AT")  +
  stat_smooth(method = "lm", col = "blue", size = 0.3) +
  theme_bw(base_size = 9) +
  theme(aspect.ratio=1#,
        #axis.text=element_text(size=7),
        #axis.title.y= element_text(size =7),
        #axis.title.x= element_text(size =7),
        #plot.margin = unit(c(0.5,1,1,1), "cm"),
        #plot.title = element_text(size=7, hjust=0.05,margin = margin(l = 10, b = -70))
        )
ggsave(filename = "figures/p_at_s.png", plot = p_at_s, width = 7, height = 7, units = "cm")

# Salinity is a predictor of AT -> using the regression defined above
d_all$at_calc <- slope_s_at * d_all$sal_fb_mix + intercept_s_at
```

@@

# add here the new periods sfinterv[..]
d_all <- d_all %>%
  dplyr::mutate(deployment_sf = ifelse(datetime >= sfinterv[1] & datetime <= sfinterv[2], 01,
                                ifelse(datetime >= sfinterv[2] & datetime <= sfinterv[3], 02,
                                ifelse(datetime >= sfinterv[3], 03, NA ))))

@@

# TODO the dataframe below is huge, cleaning it would make the script faster
calib_spectro <- cbind(calib_spectro_all, calib_spectro_10m)
kbl(calib_spectro)%>%
    kable_paper() %>% 
    kable_styling(fixed_thead = T)
```

@@

```{r, eval=FALSE, echo=FALSE, message= FALSE, warning=FALSE, out.width="80%",fig.show='hold', fig.align="center"}
# The code below is now in the "stratification" tab

@@

range_month <-
  d_all %>%
  dplyr::select(montht, sal_fb_mix, temp_insitu_11m_mix, temp_insitu_11m, pHint_tot_sf_10m) %>% 
  group_by(montht) %>%
  my_skim()
kable(range_month, caption = "")
```

@@

-   sal_fb_mix: when ferrybox data (sal_fb) are missing, they are replaced
    by data from the profiling ctd for depths > 8 m (sal_insitu_ctd_10m)

-   sal_fb_mix_interp: interpolated salinity sal_fb_mix. It is used to have as
    many spec pH to display (some are during missing data)
